\LARGE \bf Energy-Aware Dynamic Planning Algorithm for Autonomous UAVs

### 2021-01-25 icra-2021.tex
fixing indexes in the algorithm

\begin{defn}[Valid control sequence and path]\label{def:valid}
  Given a close strictly positive discrete interval $[j-n,j]$, a \emph{control sequence} $\mathbf{u}$ is \emph{valid} if for every stage $\Gamma_{i-1},\,i\in[j-n,j]$ there exist a control $\mathbf{u}_k$ that produce the next stage $\Gamma_i$.

  The path $\mathcal{P}$ resulting from a valid control sequence is a \emph{valid path}
  \begin{equation*}\begin{split}\label{eq:mission-valid}
   \mathcal{P}:=\{\mathbf{p}_{k+1}\mid&\,\exists \mathbf{u}_k,\mathbf{p}_k,\\
    &\langle\varphi_{i-1}\left(\mathbf{p}_{k}\right),\mathbf{u}_{k}\rangle\in\Gamma_{i-1}\\
    &\Longrightarrow\langle\varphi_i(\mathbf{p}_{k+1}),\mathbf{u}_{k+1}\rangle\in\Gamma_i\},
  \end{split}\end{equation*}
  where for simplicity $\langle\varphi_i(\mathbf{p}_{k}),\mathbf{u}_k\rangle:=\langle\varphi_i(\mathbf{p}_{k},c_{k}^\rho),c_{k}^\sigma\rangle$.
\end{defn}

@@

\begin{assm}\label{assm:valid}
  Given an initial plan $\Gamma$, we assume that $\exists i\in[l/n-1]^+,\,j\in[n]^+$ s.t. $\Gamma_{(i-1)n+j},\dots,\Gamma_{in+j}$ is valid.
\end{assm}

>>>>

\begin{defn}[Valid control sequence and path]\label{def:valid}
  Given a close strictly positive discrete interval $[j-n+1,j]$, a \emph{control sequence} $\mathbf{u}$ is \emph{valid} on $j$ if for every stage $\Gamma_{i-1},\,i\in[j-n+1,j]$ there exists a control $\mathbf{u}_k$ that produce the next stage $\Gamma_i$.

  The path $\mathcal{P}$ resulting from such control sequence is a \emph{valid path} on $j$
  \begin{equation*}\begin{split}\label{eq:mission-valid}
   \mathcal{P}:=\{\mathbf{p}_{k}\mid\,\exists \mathbf{u}_k,&\forall i\in[j-n+1,j]\,\\&\langle\varphi_i(\mathbf{p}_{k},c_{k}^\rho),c_{k}^\sigma\rangle\in\Gamma_i\}.
  \end{split}\end{equation*}
\end{defn}

@@

\begin{assm}[Period validity]\label{assm:valid}
  Given an initial plan $\Gamma$, we assume that $\exists i\in[l/n]^+$ s.t. the period $\Gamma_{(i-1)n+1},\dots,\Gamma_{in}$ is valid.
\end{assm}
